---
title: "SIM-tool FTP processes"
author: "BHE"
date: "December 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```


## Intro

url SIM-tool gui: http://130.139.133.47:5080/mod_perl/njobs.pl
acoount: cmst/cmst

The SIM-tool was searched for processes containing "Pikachu" and "Pika". The log-files were collected and analysed.



  
## SIM-tool activity

active export | process | errors | files sent | remarks
------------- | ------- | ------_ | ------- | ---------------------------- 
yes | alatest-to-pikachu | no | yes | Complex job uploaded 1 file.
yes | B2B-Hybris-meta_upload-ACC | no | yes |  
yes | bazaarvoice | no | yes |  | 
yes | ChannelAdvisor_si_SI | ? | no | transferred 0 files: 40 times before. Files don't seem to be processed on remote server. *Note*: One month old files can be found.
yes | CliplisterProducts | no | no | pikachu-to-clipster transferred 0 files: 1 times before. *Note*: no old files can be found.
yes | CliplisterProducts2 | no | yes | 
yes | cq5-cat_PRX_Prod | no | ? | transferred 0 files: 1 times before.
yes | cq5-meta_PRX_Stg | no | ? | transferred 0 files: 1 times before.
yes | eloqua | no | no
yes | EtailDetailProducts | no | yes | 
yes | ETLsaving_Calcu | no | yes | archive_ftp/remote (unclear) directory contains files > 1 year old. No archiving/deletions?
?   | feedcommerce | no | yes |  *Note*: old zip- and xml-files found. No archiving/deletions?
yes | feedcommerce_PL_Eirtight | no | yes | *Note*: remote dir contains file 'Apr 19  2017 DO NOT USE THIS LOCATION.txt' and zip-files from this date onward...
yes | flixmedia | no | yes | 
yes | FlixMediaProducts_DE | no | ? | pikachu-to-flixmedia transferred 0 files: 1 times before. *Note*: One month old files can be found.
yes | Hybris | no | yes | 
yes | icecat | ? | ? | *Note*: remote dir contains 2 year old files. But also recent files.
yes | IceCatRichContent | yes | yes | Job completed: pikachu-to-IceCatRichContent with 1 errors (retry of ftp put-commend for failed transfer). *Note*: remote dir contains 2 year old files. But also recent files.
?   | infomatica_tradeplace | no | yes | 
?   | lightingaws | no | yes | 
yes | Lirio | no | yes | 
?   | meta-cat-file-copy | no | no | *Note*: cp: missing destination file operand after `/applusr/pals/sim/data/pikachu-to-B2B-Hybris-meta_upload'
yes | MMDProductExport | no | yes | 
yes | myshop1 | no | no | *Note*: ssh_exchange_identification: Connection closed by remote host.  
Couldn't read packet: Connection reset by peer.
yes | rendering | no | yes | 
yes | searchstream | no | yes | 
yes | spaf | no | ? | pikachu-to-spaf transferred 0 files: 4 times before. *Note*: recent files available.
yes | WebcollageProducts | no | ? | pikachu-to-webcollage transferred 0 files: 3 times before. *Note*: recent files available.



## Missing FTP-processes for active exports

```{r data_count1, echo=FALSE, message=FALSE}
# 2. how many unique assets (based on ID) and how many occurances of each asset?
activeExports %>%
  dplyr::filter(tolower(channel) %in% 
                    tolower(c("AmaHK", "AutomotiveProductsExport",
                               "ChinaProducts", "CockpitReportExport", "EStoreProducts", 
                               "FYP", "FoxIntProducts", "FuturesourceProducts", 
                               "HomeLightMetadata", "Netbiscuits", "PhilipsRetailDirect",
                               "ProductDescription", "Tradeplace", "VmaHK", "XCProducts"
                               ))) %>%
  kableExtra::kable(caption="Active exports without FTP process") %>%
  kableExtra::kable_styling()
```
