---
title: "300_matchAwardAssets"
author: "BHE"
date: "December 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#library(XML)
library(tidyverse)
library(readr)
library(httr)
#library(purrr)
library(digest)
#library(tiff)
library(jpeg)
```

## Initial data

#
# read & list channel custom code.
#
# BHE, 26-09-2018
#

#library(XML)
library(tidyverse)
library(readr)
library(httr)
#library(purrr)
library(digest)
#library(tiff)
library(jpeg)

###############################################################################
# define data
###############################################################################
the PMT_RAW--PMT contains an AWARD-element:
```
<Award AwardType="global_highlight">
  <AwardCode>GA40019049</AwardCode>
  <AwardName>Red Dot Award 2016: winnaar</AwardName>
  <AwardDate>2016</AwardDate>
  <AwardPlace>Duitsland</AwardPlace>
  <AwardDescription>BodyGroom 1000</AwardDescription>
  <AwardAcknowledgement>Red Dot Award 2016: winnaar</AwardAcknowledgement>
  <AwardRank>2</AwardRank>
</Award>
```

This refers to an object from the ObjectAsstList

```
<Object xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <ObjectID>GA40019049</ObjectID>
  <Asset>
    <ResourceType>GAL</ResourceType>
    <Language/>
    <License>Final</License>
    <AccessRights/>
    <Modified>2016-05-11</Modified>
    <Publisher>CCR</Publisher>
    <InternalResourceIdentifier>http://pww.pcc.philips.com/mprdata/160511/1605110321_gal.jpg</InternalResourceIdentifier>
    <SecureResourceIdentifier>https://www.p4c.philips.com/cgi-bin/dcbint/sget?url=/mprdata/160511/1605110321_gal.jpg</SecureResourceIdentifier>
    <PublicResourceIdentifier/>
    <Creator>310059896</Creator>
    <Format>image/jpeg</Format>
    <Extent>136989</Extent>
    <Md5>dc6eae3c7e1f2bae83132d7af3e57436</Md5>
  </Asset>
  <Asset>
    <ResourceType>GAP</ResourceType>
    <Language/>
    <License>Final</License>
    <AccessRights/>
    <Modified>2016-05-11</Modified>
    <Publisher>CCR</Publisher>
    <InternalResourceIdentifier>http://pww.pcc.philips.com/mprdata/160511/1605110322_gap.tif</InternalResourceIdentifier>
    <SecureResourceIdentifier>https://www.p4c.philips.com/cgi-bin/dcbint/sget?url=/mprdata/160511/1605110322_gap.tif</SecureResourceIdentifier>
    <PublicResourceIdentifier/>
    <Creator>310059896</Creator>
    <Format>image/tiff</Format>
    <Extent>682256</Extent>
    <Md5>67430fd90ef639b83a5c77d89328cb72</Md5>
  </Asset>
  <Asset>
    <ResourceType>GAW</ResourceType>
    <Language/>
    <License>Final</License>
    <AccessRights/>
    <Modified>2016-05-11</Modified>
    <Publisher>CCR</Publisher>
    <InternalResourceIdentifier>http://pww.pcc.philips.com/mprdata/160511/1605110323_gaw.jpg</InternalResourceIdentifier>
    <SecureResourceIdentifier>https://www.p4c.philips.com/cgi-bin/dcbint/sget?url=/mprdata/160511/1605110323_gaw.jpg</SecureResourceIdentifier>
    <PublicResourceIdentifier/>
    <Creator>310059896</Creator>
    <Format>image/jpeg</Format>
    <Extent>2514</Extent>
    <Md5>92711a06efedb448460cf67443306c13</Md5>
  </Asset>
  <Asset>
    <ResourceType>GAZ</ResourceType>
    <Language/>
    <License>Final</License>
    <AccessRights/>
    <Modified>2017-11-28</Modified>
    <Publisher>CCR</Publisher>
    <InternalResourceIdentifier>http://pww.pcc.philips.com/mprdata/171128/17112801vt_gaz.png</InternalResourceIdentifier>
    <SecureResourceIdentifier>https://www.p4c.philips.com/cgi-bin/dcbint/sget?url=/mprdata/171128/17112801vt_gaz.png</SecureResourceIdentifier>
    <PublicResourceIdentifier/>
    <Creator/>
    <Format/>
    <Extent>474054</Extent>
    <Md5>40c6e9a37e64c8db1b8e47a7dfb86fba</Md5>
  </Asset>
</Object>
```          
Next, check if the assets defined in this ObjectAssetList are equal to the KA1-asset in the PMT that contains this AwardType
When the images are equal, it will be possible to migrate Award descriptions for the matching images into STEP.

## match images

```{r}
# data from XML
KA1_image <- 
  "http://download.p4c.philips.com/files/b/bg105_10/bg105_10_ka1_nldnl.tif"
KA1_ccrmd5 <- 
  "28ebe7b76712f9ffebc42c87f68c6f06"

GAL_image <- 
  "http://pww.pcc.philips.com/mprdata/160511/1605110321_gal.jpg"
GAL_ccrmd5 <- 
  "dc6eae3c7e1f2bae83132d7af3e57436"
GAP_image <- 
  "http://pww.pcc.philips.com/mprdata/160511/1605110322_gap.tif"
GAP_ccrmd5 <- 
  "67430fd90ef639b83a5c77d89328cb72"
GAW_image <- 
  "http://pww.pcc.philips.com/mprdata/160511/1605110323_gaw.jpg"
GAW_ccrmd5 <- 
  "92711a06efedb448460cf67443306c13"
GAZ_image <- 
  "http://pww.pcc.philips.com/mprdata/171128/17112801vt_gaz.png"
GAZ_ccrmd5 <- 
  "40c6e9a37e64c8db1b8e47a7dfb86fba"

assets <-
  data.frame(type="KA1", url=KA1_image, ccrmd5=KA1_ccrmd5) %>%
  dplyr::rbind_all(data.frame(type="GAL", url=GAL_image, ccrmd5=GAL_ccrmd5)) %>%

# calculate md5 checksum from downloaded images

```


