---
title: "Doctypes for IPL (F02) related products"
author: "Bart van Hest (Integration Technology & Services, The Future Group)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_notebook: 
    code_folding: hide
    theme: cerulean
editor_options: 
  chunk_output_type: inline
---

```{r libs_and_db_connection, warning=FALSE, include=FALSE}
#remove.packages(c("DBI", "rJava", "RJDBC"))
#install.packages('rJava', dependencies = TRUE)
#install.packages('RJDBC', dependencies = TRUE)
#install.packages('DBI', dependencies = TRUE)


# load required libraries
library(tidyverse)
library(kableExtra)

library(DBI)
# Set JAVA_HOME, set max. memory, and load rJava library
Sys.setenv(JAVA_HOME='C:/Java/jdk1.8.0_191')
options(java.parameters="-Xmx2g")
# check: https://cran.r-project.org/bin/windows/base/rw-FAQ.html
#        https://stackoverflow.com/questions/37735108/r-error-onload-failed-in-loadnamespace-for-rjava
library(rJava)

# Output Java version
.jinit()
print(.jcall("java/lang/System", "S", "getProperty", "java.version"))

# Load RJDBC library
library(RJDBC)

oracle.JdbcDriver <- 
  RJDBC::JDBC(driverClass="oracle.jdbc.OracleDriver", 
              classPath="c:/Java/Oracle/ojdbc8.jar")

pr.jdbcConnection <- 
  DBI::dbConnect(drv = oracle.JdbcDriver,
                 url = "jdbc:oracle:thin:@130.139.136.60:1521:CCR1P", 
                 user = "bvanhest", 
                 password = "Philips@123")

```

# Introduction

This report provides an overview of document types for IPL-products, with a distinction between secured and public document types.


# Data

## Overview

```{R echo=FALSE}
# /*
# select all symcure id relation related to an IPL products
# */
qry <- 
  "select count(m.pm_name) as product_count 
from m_product_model m
   , m_article_group ag
where ag.ag_cd = m.ag_cd
  and ag.mag_cd = 'F02'"

ipl_product_count <-
  DBI::dbGetQuery(conn = pr.jdbcConnection, 
                  statement = qry ) %>%
  pull(PRODUCT_COUNT)
```

The number of IPL products in CCR is `r ipl_product_count`.

The first table shows the number of assets of a specific document type that are assigned to the group of IPL products. For each document type it is shown if it is 'public' or 'restricted'.

```{r}
# /*
# select the counts per document type for all symcure id related to IPL products
# */
qry <- 
  "select sc.dt_cd as doc_type, 
decode(dt.dt_restricted_ind, 'Y', 'restricted', 'public') as availability,
count(pm.pm_name) as asset_count
from m_symptom_cure SC,
     m_symptom_cure_relation scr,
     m_document_type dt, 
     (select pm_name 
      from m_product_model m
         , m_article_group ag
      where m.ag_cd = ag.ag_cd
      and ag.mag_cd = 'F02') pm
where scr.pm_name = pm.pm_name
  and scr.sycu_id = sc.sycu_id
  and dt.dt_cd    = sc.dt_cd
group by sc.dt_cd, dt.dt_restricted_ind
order by asset_count desc"

DBI::dbGetQuery(conn = pr.jdbcConnection, 
                statement = qry ) %>%
  kableExtra::kable(caption="Asset-count per doc-type for symptom-cure records for IPL products") %>%
  kableExtra::kable_styling()
```


The second table shows the number of assets of a specific document type, but now for all products. For each document type it is shown if it is 'public' or 'restricted'.

```{r}
# /*
# select the counts per document type for all symcure id related to IPL products
# */
qry <- 
  "select sc.dt_cd as doc_type, 
decode(dt.dt_restricted_ind, 'Y', 'restricted', 'public') as availability,
count(scr.pm_name) as asset_count
from m_symptom_cure SC,
     m_symptom_cure_relation scr,
     m_document_type dt
where scr.sycu_id = sc.sycu_id
  and dt.dt_cd    = sc.dt_cd
group by sc.dt_cd, dt.dt_restricted_ind
order by asset_count desc"
 
DBI::dbGetQuery(conn = pr.jdbcConnection, 
                statement = qry ) %>%
  kableExtra::kable(caption="Asset-count per doc-type for all products") %>%
  kableExtra::kable_styling()
```



## Asset types related to IPL products

The third table presents only those IPL products that have one or more restricted assets. The number of restricted assets per product is shown. The products are ordered alphabetically.

```{r}
# /*
# Select all products that have a restricted asset linked to it
# */
qry <- 
  "select scr.pm_name as product, 
          sc.dt_cd as doc_type,
          count(sc.dt_cd) as doctype_count
from m_symptom_cure_relation scr, 
     m_symptom_cure sc,
     m_document_type dt
where scr.sycu_id=sc.sycu_id
and dt.dt_cd = sc.dt_cd
and dt.dt_restricted_ind = 'Y'
and scr.pm_name in (select pm_name 
                    from m_product_model m
                       , m_article_group ag
                    where m.ag_cd = ag.ag_cd
                    and ag.mag_cd = 'F02')
group by scr.pm_name, sc.dt_cd
order by scr.pm_name, sc.dt_cd"

#
# DON'T RUN without product selection. Takes too long to complete.
#
DBI::dbGetQuery(conn = pr.jdbcConnection, 
                statement = qry ) %>%
  kableExtra::kable(caption="IPL Products with related secured doc-types") %>%
  kableExtra::kable_styling()
```


```{r close_db_connection, warning=FALSE, include=FALSE}
# Close DB connection
dbDisconnect(pr.jdbcConnection)
```
