---
title: "Video assets"
author: "BHE"
date: "April 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Video process  CCR/Pikachu/Scene7 + beheer



## CCR Video types

master
  - CMV : Cluster Main Video - master 
  - FAV : Special doctype for Scene7 videos 

'real'
  - CVG : Campaign Video General (MP4)
  - CVI : Campaign Video Interview (MP4) 
  - CVL : Campaign Video Lifestyle (MP4)
  - CVP : Campaign Video Promotion (MP4)
  - FV1 : Family Video (MP4)
  - FV2 : Family Video (MP4)
  - FV3 : Family Video (MP4)
  - FV4 : Family Video (MP4)
  - FV5 : Family Video (MP4)
  - P3F : Product 360 Video (FLV)



## Pikachu Video types

Pikachu receives video-assets in the object_asset-list import from CCR.

Channels receiving these video-types:
```{r}
docTypesFile <-
  paste("./analyse/output","channelDocTypes.c.Rds", sep = "/")
channelDocTypes.c.df <-
  readRDS(file = docTypesFile)

# (Pikachu) video asset definitions
channelDocTypes.c.df %>%
  # remove 'channel'  column
  dplyr::select(-channel) %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 'P3F')) %>%
  # keep unique asset codes
  dplyr::distinct(code, .keep_all = TRUE) %>%
  # show as table
  kableExtra::kable(caption = "Video asset definitions in Pikachu") %>%
  kableExtra::kable_styling()
```



```{r}
docTypesFile <-
  paste("./analyse/output","channelDocTypes.wide.Rds", sep = "/")
channelDocTypes.wide.df <-
  readRDS(file = docTypesFile)

# Pikachu publication configuration
channelDocTypes.wide.df %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 'P3F')) %>%
  # remove 'description'  column
  dplyr::select(-description) %>%
  # transpose matrix (tidyverse-way)
  tidyr::gather(key = channel, value = published, SyndicationL1:XCProducts) %>% 
  tidyr::spread(key = code, value = published) %>%
  # show as table
  kableExtra::kable(caption = "Video asset's configured for Pikachu Exports") %>%
  kableExtra::kable_styling()
```
