---
title: "Video assets in (old) CMC landscape"
author: "Bart van Hest (Integration Technology & Services, The Future Group)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::html_clean:
    toc: true
    toc_depth: 4
    number_sections: true
  word_document: default
  html_document: default
  markdowntemplates::prismskel:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

# Video process CCR/Pikachu/Scene7 + maintenance



## CCR Video types

master-types

  - CMV : Cluster Main Video - master 
  - FAV : Special doctype for Scene7 videos 

'real'-types

  - CVG : Campaign Video General (MP4)
  - CVI : Campaign Video Interview (MP4) 
  - CVL : Campaign Video Lifestyle (MP4)
  - CVP : Campaign Video Promotion (MP4)
  - FML : Feature movie (with spoken or written text)
  - FQL : High quality feature movie (MP4)
  - FV1 : Family Video (MP4)
  - FV2 : Family Video (MP4)
  - FV3 : Family Video (MP4)
  - FV4 : Family Video (MP4)
  - FV5 : Family Video (MP4)
  - HQ1 : High quality movie 1 (MP4)
  - HQ2 : High quality movie 1 (MP4)
  - HQ3 : High quality movie 1 (MP4)
  - HQ4 : High quality movie 1 (MP4)
  - HQ5 : High quality movie 1 (MP4)
  - P3F : Product 360 Video (FLV)
  - P3M : 360 hotspot movie
  - P3X : Product 360 with Hotspots (js)
  - PRV : 360 View (FLV,SWF) 
  - PM2 : Product movie 2
  - PM3 : Product movie 2
  - PM4 : Product movie 2
  - PM5 : Product movie 2
  - PRM : Product movie 1 
  - SDM : Support Demonstration Movie (WMV)
  - TV1 : Tutorial movie 1 (MP4)
  - TV2 : Tutorial movie 1 (MP4)
  - TV3 : Tutorial movie 1 (MP4)
  - TV4 : Tutorial movie 1 (MP4)
  - TV5 : Tutorial movie 1 (MP4)
  
*Note*: source is the CCR [doctypes.conf](http://pww.ccr.philips.com/cgi-bin/newmpr/conf_viewer.pl?confFile=doctypes.conf&sort=2) webpage.


## Pikachu Video types

Pikachu receives video-assets in the (object_)asset-list import from CCR.

The usage of the video-assets is configured in the the file 'doctype_attributes.xml', which contains the assets included in each of the export-channels in Pikachu.

The following video-types are included in this configuration file:

```{r echo=FALSE, warning=FALSE, paged.print=FALSE}
docTypesFile <-
  paste("./output","channelDocTypes.c.Rds", sep = "/")
channelDocTypes.c.df <-
  readRDS(file = docTypesFile) %>%
  dplyr::mutate(language = as.character(language),
                secureURL = as.character(secureURL)) %>%
  # remove NA'values:
  dplyr::mutate(language = dplyr::if_else(is.na(language), '', language),
                secureURL = dplyr::if_else(is.na(secureURL), '', secureURL))

# (Pikachu) video asset definitions
channelDocTypes.c.df %>%
  # remove 'channel'  column
  dplyr::select(-channel) %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 
                            'P3F', 'P3M', 'P3X', 'PRV', 
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # keep unique asset codes and sort
  dplyr::distinct(code, .keep_all = TRUE) %>%
  dplyr::arrange(code) %>%
  # show as table
  kableExtra::kable(caption = "Video asset definitions in Pikachu") %>%
  kableExtra::kable_styling()
```

Channels receiving these video-types:

```{r echo=FALSE, warning=FALSE, paged.print=FALSE}
docTypesFile <-
  paste("./output","channelDocTypes.wide.Rds", sep = "/")
channelDocTypes.wide.df <-
  readRDS(file = docTypesFile)

# Pikachu publication configuration
channelDocTypes.wide.df %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 
                            'P3F', 'P3M', 'P3X', 'PRV', 
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # remove 'description'  column
  dplyr::select(-description) %>%
  # transpose matrix (tidyverse-way)
  tidyr::gather(key = channel, value = published, SyndicationL1:XCProducts) %>% 
  # remove NA's
  dplyr::mutate(published = dplyr::if_else(is.na(published), "", "Y")) %>%
  tidyr::spread(key = code, value = published) %>%
  # sort
  dplyr::arrange(channel) %>%
  # show as table
  kableExtra::kable(caption = "Video asset's configured for Pikachu Exports") %>%
  kableExtra::kable_styling()
```

## Pikachu processes 'using' videos

  * cmc2/webservice/pipelines
  * pipes/Scene7Videos


### cmc2/webservice/pipelines

This seemds to be old code (used for the EmpowerMe-application). According to the comment: "Used by the iPad application, security using siteminder".

`<map:match pattern="*/json**">` with parameter `getTrainingAndVideoDocuments`.



### pipes/Scene7Videos

This process exports video files to Scene7 for publication.

<map:match pattern="main/*"> with the optional parameter ```processDeletions``` Create a deletions file with deleted videos.

The assets, both the new/updated assets and the deleted assets, are queried from the Pikachu database. 

First, the export-records (customer_locale_export-table) are updated with the query `sql_createBatches.xsl`.

For product movies insert new CLE records or flag the existing records

- when MD5 is modified
- when MD5 is empty but asset mod date is after last export date
- for active products (offset days in advance)

*Note*: this assumes that all movies are locale based.

For non-product movies insert new CLE records or flag the existing records

- when MD5 is modified
- when MD5 is empty but asset mod date is after last export date

*Note*: this assumes that all movies are locale based.


Next, flag assets that were sent previously but

  - that have no active record in asset_lists
  - that were not sent as deleted (marked by the remark column)

flag is set to 2 to mark deleted assets. 





#### sql_selectAssets.xsl

```
<sql:query name="select-assets">
 select distinct al.asset_resource_ref as asset_ref
               , al.doctype
               , al.internalresourceidentifier as srcurl
               , al.format as mimetype
               , al.md5
 from customer_locale_export cle
 inner join asset_lists al
    on al.asset_resource_ref=cle.ctn
 where cle.customer_id='<xsl:value-of select="$channel"/>'
   and cle.batch=<xsl:value-of select="$batchNumber"/>
</sql:query>
```



#### sql_selectDeletedAssets.xsl

```
<sql:query name="select-deleted-assets">
 select distinct al.internalresourceidentifier as asseturl
               , al.doctype
 from customer_locale_export cle
 inner join asset_lists al
    on al.asset_resource_ref=cle.ctn
 where cle.customer_id='<xsl:value-of select="$channel"/>'
   and cle.flag = 2
</sql:query>
```

The query shows that those assets are deleted that are 

  1. related to a specific channel,
  2. with the channel flagged as '2'.
  

### Doctype selection

The doctype is selected based on the condition `where a.doctype in (<xsl:value-of select="$doctype-list"/>)`.

The variable `$doctype-list` is defined as 

```
<xsl:variable name="doctype-list">
  <xsl:text>'</xsl:text>
  <xsl:value-of select='string-join(/doctypes/doctype[attribute::*[local-name()=$channel]="yes"]/@code, "&apos;,&apos;")'/>
  <xsl:text>'</xsl:text>
</xsl:variable>
```

The xpath is applied to the document 'doctype_attributes.xml' with the value of the `$channel`-variable is 'Scene7Videos'.

The resulting doctypes are for the channel 'Scene7Videos' are:


```{r}
# (Pikachu) video asset definitions
channelDocTypes.c.df %>%
  # filter on video asset-types
  dplyr::filter(channel == 'Scene7Videos') %>%
  # keep unique asset codes
  dplyr::distinct(code, .keep_all = TRUE) %>%
  # show as table
  kableExtra::kable(caption = "Video asset definitions for Pikachu 'Scene7Videos'-channel") %>%
  kableExtra::kable_styling()
```

## Mismatch between Pikachu channels that include videos and Scene7-publication of videos

```{r filter_movies, warning=FALSE, include=FALSE}
# video export to scene7
scene7_videos <-
  channelDocTypes.c.df %>%
  # filter on video asset-types
  dplyr::filter(channel == 'Scene7Videos') %>%
  # keep unique asset codes
  dplyr::distinct(code, .keep_all = TRUE)

video_channel_usage <-
  channelDocTypes.c.df %>%
  # filter out scene7export-channel
  dplyr::filter(!channel == 'Scene7Videos') %>%
  # remove 'channel'  column (of no use after distinct)
  dplyr::select(-channel) %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 
                            'P3F', 'P3M', 'P3X', 'PRV', 
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # keep unique asset codes and sort
  dplyr::distinct(code, .keep_all = TRUE)

videos_in_channel_but_not_published_to_scene7 <-
  video_channel_usage %>%
  dplyr::anti_join(scene7_videos, by = "code")

videos_published_to_scene7_but_not_in_channel <-
  scene7_videos %>%
  dplyr::anti_join(video_channel_usage, by = "code")
```

```{r echo=FALSE, warning=FALSE}
videos_in_channel_but_not_published_to_scene7 %>%
  # present as table
  kableExtra::kable(caption = "Video's included in channels, but not published by 'Scene7Videos'-export") %>%
  kableExtra::kable_styling()
```

```{r echo=FALSE, warning=FALSE}
videos_published_to_scene7_but_not_in_channel %>%
  # present as table
  kableExtra::kable(caption = "Video's published by 'Scene7Videos'-export, but not included in channels") %>%
  kableExtra::kable_styling()
```

## Video's in Pikachu (object)asset-list imports

*data-source*: feeds in week of 2019-05-01.

```{r message=FALSE, warning=FALSE, include=FALSE}
file_name <-
  paste("./output","movies.c.Rds", sep = "/")
movies.c <-
  readRDS(file = file_name)
```

```{r echo=FALSE, warning=FALSE}
  movies.c %>%
  dplyr::group_by(source, type) %>%
  dplyr::summarise(asset_count = n_distinct(md5)) %>%
  # present as table
  kableExtra::kable(caption = "Video count per source and video-type") %>%
  kableExtra::kable_styling()
```

A quick comparison with the video-types in the feed and the ones in the configuration, shows that the following video-types are not received by Pikachu:

```{r echo=FALSE, warning=FALSE}
channelDocTypes.c.df %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 
                            'P3F', 'P3M', 'P3X', 'PRV', 
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # anti-join with tpyes in imports
  dplyr::anti_join(movies.c, by = c("code" = "type")) %>%
  dplyr::select(-channel) %>%
  dplyr::distinct(code, .keep_all = TRUE) %>%
  dplyr::arrange(code) %>%
  # present as table
  kableExtra::kable(caption = "Configured video-types not present in the Pikachu (object)asset-list import") %>%
  kableExtra::kable_styling()
```

This has an impact on the following channels:

```{r echo=FALSE, warning=FALSE}
channelDocTypes.c.df %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 
                            'P3F', 'P3M', 'P3X', 'PRV', 
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # anti-join with tpyes in imports
  dplyr::anti_join(movies.c, by = c("code" = "type")) %>%
#  dplyr::distinct(code, .keep_all = TRUE) %>%
  dplyr::select(channel, code) %>%
  dplyr::arrange(channel, code) %>%
  # present as table
  kableExtra::kable(caption = "Configured video-types not present in the Pikachu (object)asset-list import") %>%
  kableExtra::kable_styling()
```



## Video's to Scene7-export

The video's are retrieved from CCR and uploaded to the Scene7 server by the Scene7Videos-export process.


### Publication

Video-files are copied from a source to a target directory. This is controlled with two request-parameters for the Scene7Videos-export process. The mime-type is also passed as a parameter.

```
  src       The source path (pointer to asset in mprdata-dir on CCR server)
  tgt       The target path (dynamically created per asset with createScene7VideoId-function)
  mimetype  The mimetype
```

```
<!--
  Create a Scene7 ID for video files.
  The ID is based on the assets request ID (e.g. 110817012g) from CCR which is taken from the InternalResourceIdentifier.
  The ID is prefixed with a fixed string 'CCR' and has a fixed suffix '-global-001'. The doctype is added as well.
  
  E.g. http://pww.pcc.philips.com/mprdata/110817/110817012g_hq1.mp4 becomes CCR110817012G-HQ1-global-001
-->
<xsl:function name="asset-f:createScene7VideoId">
  <xsl:param name="asset-raw"/>
  
  <xsl:value-of select="concat('CCR'
                      , upper-case(replace(tokenize($asset-raw/InternalResourceIdentifier,'/')[last()],'_(.+?)$',''))
                      , '-'
                      , $asset-raw/ResourceType
                      , '-global-001'
                      )"/>
</xsl:function>
```
Once the files have been retrieved and stored in the /archive folder, a file with the name 'CONTENT-READY' is created and the movie-files will be picked up by the SIM-tool and delivered to the Scene7-server.

The SIM-tool job is called "pikachu-to-scene7-Videos-Production" and runs with a daily frequency.
Once the file '/ebizdata/pikap1/data/Scene7Videos/archive/CONTENT-READY' is present, it will move all files (movie- and (deletion)text-files) to the from the directory '/ebizdata/pikap1/data/Scene7Videos/archive' to the remote directory 'videos' on the server 's7ftp3.scene7.com'. The account 'philipsconsumer' is used.


### Removal from Publication

The Pikachu code contains a video deletion mechanism (video “un-publication”). The parameters that control this functionality are not included in the default settings for the Scene7Videos-export.

When the `processDeletions` parameter is set (boolean value?), the expor tprocess will create a deletions-file with deleted videos.

The deletion-file contains the same `tgt`-path as mentioned in the "publication"-paragraph. In this case that means that the the file contains the names of the movie-assets in the Scene7-format (i.e. 'CCR110817012G-HQ1-global-001' in the example from the "publication"-paragraph).

?? What happens with the deletions-file ??
--> It's also uploaded to the Scene7-server by the SIM-tool.

