---
title: "Video assets in (old) CMC landscape"
author: "Bart van Hest (Integration Technology & Services, The Future Group)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::html_clean:
    toc: true
    toc_depth: 4
    number_sections: true
  word_document: default
  html_document: default
  markdowntemplates::prismskel:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

# Video process CCR/Pikachu/Scene7 + maintenance



## CCR Video types

master-types

  - CMV : Cluster Main Video - master 
  - FAV : Special doctype for Scene7 videos 

'real'-types

  - CVG : Campaign Video General (MP4)
  - CVI : Campaign Video Interview (MP4) 
  - CVL : Campaign Video Lifestyle (MP4)
  - CVP : Campaign Video Promotion (MP4)
  - FML : Feature movie (with spoken or written text)
  - FQL : High quality feature movie (MP4)
  - FV1 : Family Video (MP4)
  - FV2 : Family Video (MP4)
  - FV3 : Family Video (MP4)
  - FV4 : Family Video (MP4)
  - FV5 : Family Video (MP4)
  - HQ1 : High quality movie 1 (MP4)
  - HQ2 : High quality movie 1 (MP4)
  - HQ3 : High quality movie 1 (MP4)
  - HQ4 : High quality movie 1 (MP4)
  - HQ5 : High quality movie 1 (MP4)
  - P3F : Product 360 Video (FLV)
  - PM2 : Product movie 2
  - PM3 : Product movie 2
  - PM4 : Product movie 2
  - PM5 : Product movie 2
  - PRM : Product movie 1 
  - SDM : Support Demonstration Movie (WMV)
  - TV1 : Tutorial movie 1 (MP4)
  - TV2 : Tutorial movie 1 (MP4)
  - TV3 : Tutorial movie 1 (MP4)
  - TV4 : Tutorial movie 1 (MP4)
  - TV5 : Tutorial movie 1 (MP4)
  
*Note*: source is the CCR [doctypes.conf](http://pww.ccr.philips.com/cgi-bin/newmpr/conf_viewer.pl?confFile=doctypes.conf&sort=2) webpage.


## Pikachu Video types

Pikachu receives video-assets in the (object_)asset-list import from CCR.

The usage of the video-assets is configured in the the file 'doctype_attributes.xml', which contains the assets included in each of the export-channels in Pikachu.

The following video-types are included in this configuration file:

```{r echo=FALSE, warning=FALSE, paged.print=FALSE}
docTypesFile <-
  paste("./output","channelDocTypes.c.Rds", sep = "/")
channelDocTypes.c.df <-
  readRDS(file = docTypesFile) %>%
  dplyr::mutate(language = as.character(language),
                secureURL = as.character(secureURL)) %>%
  # remove NA'values:
  dplyr::mutate(language = dplyr::if_else(is.na(language), '', language),
                secureURL = dplyr::if_else(is.na(secureURL), '', secureURL))

# (Pikachu) video asset definitions
channelDocTypes.c.df %>%
  # remove 'channel'  column
  dplyr::select(-channel) %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 'P3F',
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # keep unique asset codes and sort
  dplyr::distinct(code, .keep_all = TRUE) %>%
  dplyr::arrange(code) %>%
  # show as table
  kableExtra::kable(caption = "Video asset definitions in Pikachu") %>%
  kableExtra::kable_styling()
```

Channels receiving these video-types:

```{r echo=FALSE, warning=FALSE, paged.print=FALSE}
docTypesFile <-
  paste("./output","channelDocTypes.wide.Rds", sep = "/")
channelDocTypes.wide.df <-
  readRDS(file = docTypesFile)

# Pikachu publication configuration
channelDocTypes.wide.df %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 'P3F',
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # remove 'description'  column
  dplyr::select(-description) %>%
  # transpose matrix (tidyverse-way)
  tidyr::gather(key = channel, value = published, SyndicationL1:XCProducts) %>% 
  # remove NA's
  dplyr::mutate(published = dplyr::if_else(is.na(published), "", "Y")) %>%
  tidyr::spread(key = code, value = published) %>%
  # sort
  dplyr::arrange(channel) %>%
  # show as table
  kableExtra::kable(caption = "Video asset's configured for Pikachu Exports") %>%
  kableExtra::kable_styling()
```

## Pikachu processes 'using' videos

  * cmc2/webservice/pipelines
  * pipes/Scene7Videos


### cmc2/webservice/pipelines

This seemds to be old code (used for the EmpowerMe-application). According to the comment: "Used by the iPad application, security using siteminder".

`<map:match pattern="*/json**">` with parameter `getTrainingAndVideoDocuments`.



### pipes/Scene7Videos

This process exports video files to Scene7 for publication.

<map:match pattern="main/*"> with the optional parameter ```processDeletions``` Create a deletions file with deleted videos.

The assets, both the new/updated assets and the deleted assets, are queried from the Pikachu database. 

First, the export-records (customer_locale_export-table) are updated with the query `sql_createBatches.xsl`.

For product movies insert new CLE records or flag the existing records

- when MD5 is modified
- when MD5 is empty but asset mod date is after last export date
- for active products (offset days in advance)

*Note*: this assumes that all movies are locale based.

For non-product movies insert new CLE records or flag the existing records

- when MD5 is modified
- when MD5 is empty but asset mod date is after last export date

*Note*: this assumes that all movies are locale based.


Next, flag assets that were sent previously but

  - that have no active record in asset_lists
  - that were not sent as deleted (marked by the remark column)

flag is set to 2 to mark deleted assets. 





#### sql_selectAssets.xsl

```
<sql:query name="select-assets">
 select distinct al.asset_resource_ref as asset_ref
               , al.doctype
               , al.internalresourceidentifier as srcurl
               , al.format as mimetype
               , al.md5
 from customer_locale_export cle
 inner join asset_lists al
    on al.asset_resource_ref=cle.ctn
 where cle.customer_id='<xsl:value-of select="$channel"/>'
   and cle.batch=<xsl:value-of select="$batchNumber"/>
</sql:query>
```



#### sql_selectDeletedAssets.xsl

```
<sql:query name="select-deleted-assets">
 select distinct al.internalresourceidentifier as asseturl
               , al.doctype
 from customer_locale_export cle
 inner join asset_lists al
    on al.asset_resource_ref=cle.ctn
 where cle.customer_id='<xsl:value-of select="$channel"/>'
   and cle.flag = 2
</sql:query>
```

The query shows that those assets are deleted that are 

  1. related to a specific channel,
  2. with the channel flagged as '2'.
  

### Doctype selection

The doctype is selected based on the condition `where a.doctype in (<xsl:value-of select="$doctype-list"/>)`.

The variable `$doctype-list` is defined as 

```
<xsl:variable name="doctype-list">
  <xsl:text>'</xsl:text>
  <xsl:value-of select='string-join(/doctypes/doctype[attribute::*[local-name()=$channel]="yes"]/@code, "&apos;,&apos;")'/>
  <xsl:text>'</xsl:text>
</xsl:variable>
```

The xpath is applied to the document 'doctype_attributes.xml' with the value of the `$channel`-variable is 'Scene7Videos'.

The resulting doctypes are for the channel 'Scene7Videos' are:


```{r}
# (Pikachu) video asset definitions
channelDocTypes.c.df %>%
  # filter on video asset-types
  dplyr::filter(channel == 'Scene7Videos') %>%
  # keep unique asset codes
  dplyr::distinct(code, .keep_all = TRUE) %>%
  # show as table
  kableExtra::kable(caption = "Video asset definitions for Pikachu 'Scene7Videos'-channel") %>%
  kableExtra::kable_styling()
```

## Mismatch between Pikachu channels that include videos and Scene7-publication of videos

```{r filter_movies, include=FALSE}
# video export to scene7
scene7_videos <-
  channelDocTypes.c.df %>%
  # filter on video asset-types
  dplyr::filter(channel == 'Scene7Videos') %>%
  # keep unique asset codes
  dplyr::distinct(code, .keep_all = TRUE)

video_channel_usage <-
  channelDocTypes.c.df %>%
  # filter out scene7export-channel
  dplyr::filter(!channel == 'Scene7Videos') %>%
  # remove 'channel'  column (of no use after distinct)
  dplyr::select(-channel) %>%
  # filter on video asset-types
  dplyr::filter(code %in% c('CVG', 'CVI', 'CVL', 'CVP', 'FML', 'FQL', 
                            'FV1', 'FV2', 'FV3', 'FV4', 'FV5', 
                            'HQ1', 'HQ2', 'HQ3', 'HQ4', 'HQ5', 'P3F',
                            'PM2', 'PM3', 'PM4', 'PM5', 'PRM', 'SDM',
                            'TV1', 'TV2','TV3','TV4','TV5')) %>%
  # keep unique asset codes and sort
  dplyr::distinct(code, .keep_all = TRUE)

videos_in_channel_but_not_published_to_scene7 <-
  video_channel_usage %>%
  dplyr::anti_join(scene7_videos, by = "code")

videos_published_to_scene7_but_not_in_channel <-
  scene7_videos %>%
  dplyr::anti_join(video_channel_usage, by = "code")
```

```{r echo=FALSE}
videos_in_channel_but_not_published_to_scene7 %>%
  # present as table
  kableExtra::kable(caption = "Video's included in channels, but not published by 'Scene7Videos'-export") %>%
  kableExtra::kable_styling()
```

```{r echo=FALSE}
videos_published_to_scene7_but_not_in_channel %>%
  # present as table
  kableExtra::kable(caption = "Video's published by 'Scene7Videos'-export, but not included in channels") %>%
  kableExtra::kable_styling()
```
